%-------------------------
% Resume: Khush Patel — Exact Ammar Meman layout
%-------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{array}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames]{color}
\usepackage{paracol}
\usepackage{microtype}
\input{glyphtounicode}

\geometry{
  top=0.35in,
  bottom=0.35in,
  left=0.38in,
  right=0.38in
}

\pagestyle{empty}
\urlstyle{same}
\pdfgentounicode=1

% Section title style — small caps + rule, like Ammar
\titleformat{\section}{
  \vspace{-8pt}\small\bfseries\scshape\raggedright
}{}{0em}{}[\vspace{-2pt}\rule{\linewidth}{0.4pt}\vspace{-4pt}]

\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=1pt, parsep=0pt}

%============================================================
\begin{document}

%----------HEADING----------
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge KHUSH PATEL} & Phone: +91 9409223427 \\
  \textit{FULL STACK DEVELOPER \& SOFTWARE ENGINEER} & Email: \href{mailto:khushpatel9979@gmail.com}{khushpatel9979@gmail.com} \\
  & Location: Ahmedabad, Gujarat, India \\
\end{tabular*}

\vspace{2pt}
\noindent\hrule
\vspace{2pt}

% Social links row
\noindent
\begin{tabular*}{\textwidth}{l@{\hspace{18pt}}l@{\hspace{18pt}}l@{\hspace{18pt}}l}
  \href{https://linkedin.com/in/khushpatel9979}{\underline{LinkedIn}} &
  \href{https://github.com/KHUSHPATEL143}{\underline{Github}} &
  \href{https://khushpatel.online}{\underline{Portfolio}} &
  \href{https://leetcode.com/u/nOx8HAyDTE/}{\underline{LeetCode}} \\
\end{tabular*}

\vspace{2pt}
\noindent\hrule
\vspace{4pt}

%----------TWO-COLUMN BODY (LEFT 36% | RIGHT 64%)----------
\setlength{\columnsep}{14pt}
\columnratio{0.36}
\begin{paracol}{2}

%==========================
% LEFT COLUMN
%==========================

\section{Skills}

\textbf{Languages \& Frameworks} \\
\small JavaScript (ES6+), TypeScript, C++, React.js, Next.js, Node.js, Tailwind CSS, HTML5, CSS3 \par

\vspace{5pt}
\textbf{Databases \& Backend} \\
\small MongoDB, Supabase, REST APIs, Express.js \par

\vspace{5pt}
\textbf{Deployment} \\
\small Vercel, Netlify, Render \par

\vspace{5pt}
\textbf{Tools \& Platforms} \\
\small Postman, Figma, N8N, VS Code, npm, Git, GitHub \par

\vspace{5pt}
\textbf{AI \& Automation} \\
\small Gemini API, N8N Workflow Automation \par

\vspace{6pt}

\section{Hackathons \& Awards}

\textbf{1. CodingGita Hackathon} \\
\small \textbf{Winner (1st Rank)} \hfill \textit{June 2026} \\
\small Built \textbf{Lakshya} — an AI browser companion that reduces context switching by allowing users to chat with the current page, summarize content, analyze PDFs, and explain code inside the active tab. \par

\vspace{5pt}
\textbf{2. OceanLab x CHARUSAT} \\
\small \textbf{Finalist (among 250+ teams)} \hfill \textit{Apr 2026} \\
\small Built \textbf{IdeaForge} — MERN SaaS workspace. Selected for an interview round by OceanLab, declined to stay focused on the development journey. \par

\vspace{5pt}
\textbf{3. DAIICT Hackathon} \hfill \textit{2026} \\
\small Participated with \textbf{Talentra} — a multi-agent resume intelligence and candidate-job matching platform. \par

\vspace{5pt}
\textbf{4. SU Hackathon} \hfill \textit{2026} \\
\small Participated with \textbf{Electrosphere} Face Recognition backend and Flask API embedding generator. \par

\vspace{6pt}

\section{Certifications}

\textbf{Software Engineering Simulations} \par
\vspace{2pt}
\small Walmart Adv. Software Eng. \\
\small AWS Solutions Architecture \\
\small AI Workplace Simulation \\
\small SoloLearn — JavaScript Advanced \par

\vspace{5pt}
\textbf{Hackathon Participations} \par
\vspace{2pt}
\small ArtPark CodeForge (IISc) \\
\small Synaptix AI (IIT Madras) \\
\small Singularity AI (IIT Dharwad) \\
\small HACKSAGON (IIITM) \\
\small Dev Heat (IIIT Surat) \\
\small Odoo x Adani Hackathon \\
\small Elite Hack 1.0 \quad Bitathon (GIM Goa) \par

%==========================
% RIGHT COLUMN
%==========================
\switchcolumn

\section{Education}

\noindent\textbf{Swaminarayan University, Kalol} \hfill \textit{2025--2029} \\
\small BE in Computer Engineering \enspace | \enspace Sem 1: 9.33 SGPA \par

\vspace{4pt}
\noindent\textbf{Glorious Public School} \hfill \textit{2025 / 2023} \\
\small Higher Secondary (12th) \enspace \& \enspace Secondary Education (10th) \par

\vspace{6pt}

\section{Professional Summary}

\small Computer Engineering student and Full-Stack Developer who learns fast and builds faster. Proficient in JavaScript, React.js, Node.js, and MongoDB, with hands-on experience shipping production-grade applications and AI-integrated products. Sharp problem-solving instincts built through consistent DSA practice and multiple national-level hackathon participations. Always focused on writing clean code, building intuitive interfaces, and delivering things that actually work. \par

\vspace{6pt}

\section{Experience}

\noindent\textbf{Full-Stack Developer (Independent / Hackathons)} \\
\small 2025 -- Present \enspace | \enspace Self-Employed \par
\vspace{2pt}
\begin{itemize}
  \item \small Engineered \textbf{5+ full-stack web applications} using React.js, Node.js, Express.js \& MongoDB, each deployed to production.
  \item \small Developed \textbf{10+ scalable RESTful API endpoints} with JWT authentication, optimizing database queries for performance.
  \item \small Built \textbf{5+ automation projects} using N8N and AI APIs, streamlining client workflows end-to-end.
  \item \small Solving Data Structures and Algorithms problems on LeetCode — arrays, strings, trees, and graph patterns.
  \item \small Architected a full-stack educational management platform with role-based access for teachers and students.
  \item \small Implemented real-time analytics dashboard to track student attendance and performance metrics.
  \item \small Engineered a GitHub profile explorer with real-time API integration and light/dark theme toggle.
  \item \small Shipped IdeaForge — an AI startup workspace — within a 48-hour hackathon at CHARUSAT.
\end{itemize}

\vspace{6pt}

\section{Projects}

\noindent\textbf{1. IdeaForge} \hfill \href{https://crmideaforge.onrender.com}{\small\underline{Live}} \enspace \href{https://github.com/KHUSHPATEL143/ideaForge}{\small\underline{Github}}
\begin{itemize}
  \item \small AI-powered startup workspace — idea scoring, role-based teams, task \& finance tracking, Gmail \& Calendar integration, team chat, and a natural-language Command Centre.
  \item \small Built with Next.js and Supabase; deployed and production-ready.
\end{itemize}

\vspace{4pt}
\noindent\textbf{2. ECC Frontend} \hfill \href{https://ecc-gamma.vercel.app/}{\small\underline{Live}} \enspace \href{https://github.com/KHUSHPATEL143/ECC-frontend}{\small\underline{Github}}
\begin{itemize}
  \item \small Investment club dashboard focusing on polished UI flows, installment tracking, and admin workflows.
  \item \small Built with React, Vite, Tailwind CSS, and Recharts.
\end{itemize}

\vspace{4pt}
\noindent\textbf{3. Vrestro} \hfill \href{https://restaurant-oc42.vercel.app/}{\small\underline{Live}} \enspace \href{https://github.com/KHUSHPATEL143/Vrestro}{\small\underline{Github}}
\begin{itemize}
  \item \small Restaurant ordering system handling customer ordering, manager operations, kitchen display, and inventory.
  \item \small Built with a React frontend and Node/Express backend.
\end{itemize}

\vspace{4pt}
\noindent\textbf{4. Projects \& Clones Collection} \hfill \href{https://projectsandclone.vercel.app/}{\small\underline{Live}} \enspace \href{https://github.com/KHUSHPATEL143/Projects_and-_CloneinHTML-CSS-JS}{\small\underline{Github}}
\begin{itemize}
  \item \small 5+ pixel-perfect frontend clones using CSS Grid and Flexbox; semantic HTML, responsive design, cross-browser compatible.
\end{itemize}

\end{paracol}

\end{document}
